PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-21 paper.tex
WIP on the abstract

Child-robot interactions are increasingly being explored in domains which
require longer-term application, such as healthcare and education. In order
for a robot to behave in an appropriate manner over longer timescales, its
behaviours should be coterminous with that of the interacting children.
Generating such sustained and engaging social behaviours is an on-going research
challenge, and we argue here that the recent progress of deep machine learning
opens new perspectives that the HRI community should embrace. As an initial
step in that direction, we present a new large and open dataset of
children social interactions, designed with deep-learning applications in mind.
Our acquisition methodology relies on little-constrainted \emph{free play}:
by doing so, we seek to capture a rich set of behavioural patterns occurring
in natural social interactions.

>>>>

Child-robot interactions are increasingly being explored in domains which
require longer-term application, such as healthcare and education. In order
for a robot to behave in an appropriate manner over longer timescales, its
behaviours should be coterminous with that of the interacting children.
Generating such sustained and engaging social behaviours is an on-going research
challenge, and we argue here that the recent progress of deep machine learning
opens new perspectives that the Human-Robot Interaction (HRI) community
should embrace.

As an initial step in that direction, we introduce a novel
open dataset of children social interactions, designed with
deep-learning applications in mind. Our acquisition methodology relies on
engaging and purposefully underspecified \emph{free play} situations. By doing
so, we capture a rich set of behavioural patterns occurring in natural
social interactions. Learning to recognise (and generate) automatically such
behaviours is one of the ambitious foreseen outcome that this dataset enables.
